Type Error Telemetry at Scale

### 2023-09-23 programming23/paper.tex
related work table, again

  \FILL{}

  \begin{tabular}{l@{~}cccccc}
    &               & Code      & Session ID & Timestamp     & Deterministic (???) & Private Data (???) \\\midrule
    & Transparent   & \chkNo    & \chkNo     & \chkNo        & \chkYes       & \chkNo      \\
  * & Roblox Studio & \chkNo    & \chkYes    & \chkNo        & \chkNo        & \chkYes     \\
%% orthogonal %%    & Diff.Priv     & $\epsilon$ & \chkYes   & \chkYes       & \chkYes       & \chkYes     \\
%% orthogonal %%    & CBI           & \chkMaybe & \chkMaybe  & \chkNo        & \chkNo        & ?           \\
    & Classic       & \chkYes   & \chkYes    & \chkYes       & \chkYes       & \chkYes     \\
  \end{tabular}
\end{table}

>>>>

  \begin{tabular}{l@{~~}c@{~~}c@{~~}c@{~~}c@{~~}c}
    ~             & Event Counts & Random  & Timestamps & Error Msgs. & Source Code \\\midrule
    Roblox Studio & \chkYes      & \chkYes & \chkYes    & \chkNo        & \chkNo    \\
    Transparent   & \chkYes      & \chkNo  & \chkNo     & \chkNo        & \chkNo    \\
    Classic       & \chkYes      & \chkNo  & \chkYes    & \chkYes       & \chkYes   \\
%% orthogonal %%    & Diff.Priv
%% orthogonal %%    & CBI
  \end{tabular}
\end{table}
